Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-04-28 03-SCPME.Rmd
fixed split rendering bug

\begin{align}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
\end{align}

@@

\begin{equation}
\begin{split}
  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ g\left(Z^{k}\right) + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)' Q\left(\Omega - \Omega^{k}\right)
(\#eq:approx)
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
(\#eq:augADMM)\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 \right\|_{F}
(\#eq:scpmestopping)\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  l\left( \Omega_{y | x}, \Omega_{x}, \Sigma_{xy} | Y, X \right) &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)\left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)'\Omega_{y | x} \right] \\
  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}'\Omega_{x} \right) \\
  &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega_{x} \right| - \frac{n}{2}tr\left( S_{x}\Omega_{x} \right)
(\#eq:partialjointloglik)\notag
\end{split}
\end{equation}

@@

\begin{equation}
\begin{split}
  \hat{\Omega}_{x} &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S_{x}\Omega_{x} \right) - \frac{n}{2}\log\left| \Omega_{x} \right| \right\} \\
  &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{1}{n}\left\| \left( \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
(\#eq:omegajointloglik)\notag
\end{split}
\end{equation}

>>>>

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}L_{\rho}(\Omega, Z^{k}, \Lambda^{k}) \\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}L_{\rho}(\Omega^{k + 1}, Z, \Lambda^{k}) \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
\end{split}
(#\eq:augmentedprecision)
\end{equation}

@@

\begin{equation}
\begin{split}
  \tilde{L}_{\rho}\left(\Omega, Z^{k}, \Lambda^{k}\right) = f\left(\Omega\right) &+ g\left(Z^{k}\right) + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \\
  &+ \frac{\rho}{2}vec\left(\Omega - \Omega^{k}\right)' Q\left(\Omega - \Omega^{k}\right)
\end{split}
(\#eq:approx)
\end{equation}

@@

\begin{equation}
\begin{split}
  \Omega^{k + 1} &= \arg\min_{\Omega \in \mathbb{S}_{+}^{p}}\left\{tr\left[\left(S + G^{k}\right)\Omega\right] - \log\left|\Omega\right| + \frac{\rho\tau}{2}\left\|\Omega - \Omega^{k}\right\|_{F}^{2} \right\}\\
  Z^{k + 1} &= \arg\min_{Z \in \mathbb{R}^{n \times r}}\left\{\lambda\left\|Z\right\|_{1} + tr\left[(\Lambda^{k})'(A\Omega B - Z^{k} - C) \right] + \frac{\rho}{2}\left\|A\Omega B - Z^{k} - C \right\|_{F}^{2} \right\} \\
  \Lambda^{k + 1} &= \Lambda^{k} + \rho\left(A\Omega^{k + 1}B - Z^{k + 1} - C \right)
\end{split}
(\#eq:augADMM)\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  \epsilon^{pri} &= \sqrt{nr}\epsilon^{abs} + \epsilon^{rel}\max\left\{ \left\| A\Omega^{k + 1}B \right\|_{F}, \left\| Z^{k + 1} \right\|_{F}, \left\| C \right\|_{F} \right\} \\
  \epsilon^{dual} &= p\epsilon^{abs} + \epsilon^{rel}\left\| \left( B(\Lambda^{k + 1})'A + A'\Lambda^{k + 1}B' \right)/2 \right\|_{F}
\end{split}
(\#eq:scpmestopping)\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  l\left( \Omega_{y | x}, \Omega_{x}, \Sigma_{xy} | Y, X \right) &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}\sum_{i = 1}^{n} tr\left[ \left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)\left( Y_{i} - \Sigma_{xy}'\Omega_{x} X_{i} \right)'\Omega_{y | x} \right] \\
  &+\frac{n}{2}\log\left| \Omega \right| - \frac{1}{2}\sum_{i = 1}^{n}tr\left( X_{i}X_{i}'\Omega_{x} \right) \\
  &= constant + \frac{n}{2}\log\left| \Omega_{y | x} \right| - \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{y | x} \right)\Omega_{y | x} \right] \\
  &+ \frac{n}{2}\log\left| \Omega_{x} \right| - \frac{n}{2}tr\left( S_{x}\Omega_{x} \right)
\end{split}
(\#eq:partialjointloglik)\notag
\end{equation}

@@

\begin{equation}
\begin{split}
  \hat{\Omega}_{x} &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ \frac{1}{2}tr\left[ \left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)'\left( \mathbb{Y} - \mathbb{X}\Omega_{x}\Sigma_{xy} \right)\Omega_{y | x} \right] + \frac{n}{2}tr\left( S_{x}\Omega_{x} \right) - \frac{n}{2}\log\left| \Omega_{x} \right| \right\} \\
  &= \arg\min_{\Omega_{x} \in \mathbb{S}_{+}^{p}}\left\{ tr\left( S_{x}\Omega_{x} \right) - \log\left| \Omega_{x} \right| + \frac{1}{n}\left\| \left( \mathbb{X}\Omega_{x}\Sigma_{xy} - \mathbb{Y} \right)\Omega_{y | x}^{1/2} \right\|_{F}^{2} \right\}
\end{split}
(\#eq:omegajointloglik)\notag
\end{equation}
